\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[a4paper, margin=1in]{geometry}
\usepackage{xcolor}
\large
\title{Homework \# 1}

\begin{document}
\begin{titlepage}
	\begin{center}
    \line(1,0){300}\\
    [0.65cm]
	\huge{\bfseries Homework \# 1}\\
	\line(1,0){300}\\
	\textsc{\LARGE A/B Testing}\\
	\textsc{\LARGE  Fall 2023}\\
	[5.5cm]
	\textsc{\LARGE NAMES: names of all students here}\\
	\textsc{\LARGE ANDREW IDs: Andrew IDs of all students here}\\
	[1.5cm]
	\textsc{\LARGE One student submits homework on Gradescope}\\
	\textsc{\LARGE Then add other students as team members}\\
	[5.5cm]
	\textsc{DUE November 7, 5.00pm EST}\\
	[0.5cm]
	\textsc{\large Show your work as part of your answers.\\Include code and outputs as needed (screen captures are enough).\\Cite all your sources (human generated and otherwise).}\\
	\end{center}
\end{titlepage}

\section*{\color{black} Question 1 {\bf [60 points]}}

Define the following concepts using your own words: {\bf [10 points each]}\\

a) Counterfactual\\

b) Selection\\

c) Causal effect\\

d) Back door\\

e) Randomized Controlled Trial\\

f) Pre-experimental balance\\

\vspace{1cm}

{\color{blue}

Type your answer here!
}\\

\section*{\color{black} Question 2 {\bf [90 points]}}

A team on analysts are trying to find the effect of allowing smartphones into the classroom on the performance of students. For this purpose, a school shared data with this team, available to you for the purpose of this homework in file HW-1-a.csv. Several students in the school were subject to different conditions during one lecture, namely:\\

B: smartphones banned from the classroom\\

ANL: smartphones allowed into the classroom but not used to assist instruction\\

AML: smartphones allowed into the classroom and used to assist instruction\\

Using the smartphones to assist instruction was accomplished by having the teacher actively asking the students to use the devices to complement learning while in the classroom. The following covariates are included in this file:\\

stu\_id: an anonimized identifier for each student\\

treatment ("B","ANL","AML"): experimental condition as described above\\

prescore (0-100): the grade students had in a test given at the beginning of the lecture\\

postscore (0-100): the grade students had in a test given at the end of the lecture\\

female: an indicator for gender (TRUE-female, FALSE-otherwise)\\

Use this dataset to answer the following questions:\\

a) How many students are included in this dataset and in each condition? {\bf [2+2 points]}\\

b) Show descriptive statistics for the improvement in test scores from the pre-test to the post-test {\bf [16 points]}\\

c) Show whether the improvement in the scores (as defined above) reduced when smartphones were allowed into the classroom and not used to assist instruction (compared to when they were banned from the classroom) {\bf [20 points]}\\

d) Show whether the improvement in the scores (as defined above) increased when smartphones were allowed into the classroom and used to assist instruction (compared to when they were banned from the classroom) {\bf [20 points]}\\

e) Are the effects computed in d) and e) causal? Why or why not? Show suggestive empirical evidence to support your conclusion {\bf [5+10+15 points]}\\

(note: if you are running regressions (and depending on the software you use) it may be helpful to transform categorical variables (like treatment and female) into numerical types).

\vspace{1cm}

{\color{blue}

Type your answer here!
}\\

\section*{\color{black} Question 3 {\bf [100 points]}}

Later on, the team of analysts arranged to run an experiment with this school to find the causal effect discussed in the previous question. The school agreed to use a subset of its students to participate in the experiment. Students were randomly assigned to the 3 experimental conditions referred above during one lecture. The school shared the dataset in file HW-1-b.csv available to you for the purpose of this homework. Use this dataset to answer the following questions:\\

a) How many students participated in the experiment in each condition? How many of them are female? {\bf [2+2 points]}\\

b) Show suggestive evidence that this data came from a well executed RCT {\bf [15 points]}\\

c) Show descriptive statistics for the improvement in test scores from the pre-test to the post-test {\bf [16 points]}\\

d) Show whether the improvement in the scores (as defined above) reduced when smartphones were allowed into the classroom and not used to assist instruction (compared to when they were banned from the classroom)? {\bf [20 points]}\\

e) Show whether the improvement in the scores (as defined above) increased when smartphones were allowed into the classroom and used to assist instruction (compared to when they were banned from the classroom)? {\bf [20 points]}\\

f) Show whether the results obtained in d) and e) above are different for female and male students {\bf [25 points]}\\ 

\vspace{1cm}

{\color{blue}

Type your answer here!
}\\

\end{document}